---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sparklio

<!-- badges: start -->
<!-- badges: end -->

`{sparklio}` extends the `{sparklyr}` IO interface by providing a faster and cleaner interface for pushing and pulling data between R and Spark amongst other things.

## Installation

You can install the development version of `{sparklio}` from [GitHub](https://github.com/nathaneastwood/sparklio) with:

``` r
# install.packages("remotes")
remotes::install_github("nathaneastwood/sparklio")
```

## Usage

```{r}
library(sparklio)
sc <- sparklyr::spark_connect(master = "local")
```

`{sparklio}` allows the user to:

* push data from R to Spark:

```{r}
# This is equivalent to dplyr::copy_to() but it faster
mtcars_spark <- spark_push_data(sc, mtcars, "mtcars")
```

* pull data from Spark into R:

```{r}
mtcars <- spark_pull_data(mtcars, sc)
mtcars <- spark_pull_data("mtcars", sc)
mtcars <- spark_pull_data(mtcars_spark)
```

* query data in Spark

```{r}
mpg <- spark_query_data(
  sc,
  "SELECT mpg FROM mtcars",
  type = "lazy",
  name = "mpg"
)
```

```{r}
mpg <- spark_query_data(
  sc,
  "SELECT mpg FROM mtcars",
  type = "compute",
  name = "mpg"
)
```

```{r}
mpg <- spark_query_data(
  sc,
  "SELECT mpg FROM mtcars",
  type = "collect"
)
```

* drop data from Spark

```{r}
spark_drop_table(sc, "mtcars")
```
